Measuring Individual Partisan Harm in Redistricting

### 2021-09-13 paper/paper.Rmd
equity ideas

<!--  Section 1 here should really be what we're interested in I think -->

@@

As with the utility measures, this harm measure naturally extends to multiple elections and districting plans.
Make the counterfactual plan a random variable $\tilde Q$, with $(V,Q,\tilde Q)\sim\pi$ such that $Q\indep\tilde Q$.
Then the harm to a random voter is $H \dfeq h(I, V, Q, \tilde Q)$.

>>>>

@@

```{=html}
<!--  
With Harm defined, we can thus define Partisan Equity as: $E[H|V(I) = DEM] = E[H|V(I) = REP]$

Thus Fairness can be described as the signed movement away from equity. This naming works because it's condition on the votes and geographic distribution that you have, rather than some neutral midpoint that would be hard to justify.

This clarifies our QOI and by later focusing on fairness, that gives us the analogous connection between bias (symmetry) and fairness (equity).

Later, that also gives room in the discussion of the EGAP to talk about why you could describe a utility function based on $Pr(Vote not wasted)$, which 
-->
```
As with the utility measures, this harm measure naturally extends to multiple elections and districting plans.
Make the counterfactual plan a random variable $\tilde Q$, with $(V,Q,\tilde Q)\sim\pi$ such that $Q\indep\tilde Q$.
Then the harm to a random voter is $H \dfeq h(I, V, Q, \tilde Q)$.
